% ===============
% Quote
% ===============
%\cvsection{Favourite Quote}

% \medskip
% \begin{quote}
% ``Don’t be afraid of new arenas.''
%  -- Elon
% \end{quote}
% \vspace{1.5mm}
% \medskip


\cvsection{About Me}


I am a passionate technologist with over 10 years of experience in
Infrastructure Administration and Web Development.
My colleagues would
describe me as
{\color{accent}creative},
{\color{accent}solution oriented},
and always {\color{accent}motivated}.

\vspace{1.9mm}

When I'm not at work I will most likely be climbing mountain tops, exploring new places or
enjoying the peace in mind when meditating, jogging or working out.

% ===============
% Skills
% ===============

%\cvsection{Strengths}
%\begin{spacing}{1.4}
%\cvtag{Motivation}
% \cvtag{Coaching people}
%\cvtag{Adaptability}
%\cvtag{Learning agility}
%\cvtag{Creativity}
% \cvtag{Strong Analytical abilities}
%\end{spacing}

\cvsection{Skills}%

\makebox[0pt][l]{%
  \hspace{1.5cm}
  \raisebox{-\totalheight}[0pt][0pt]{%
   {\color{background}\fontsize{250}{48}\faLaptop}
}}%
Requirements Engineering \hfill\SLIDER{2.5cm}{0.9}\vspace{0.3cm}

Project Management \hfill\SLIDER{2.5cm}{0.6}\vspace{0.3cm}

Scrum \& Kanban \hfill\SLIDER{2.5cm}{0.8}\vspace{0.3cm}

JavaScript ES6 \hfill\SLIDER{2.5cm}{0.9}\vspace{0.3cm}

NodeJS \hfill\SLIDER{2.5cm}{0.6}\vspace{0.3cm}

React \& Redux \hfill\SLIDER{2.5cm}{0.8}\vspace{0.3cm}

Vue \& Vuex \hfill\SLIDER{2.5cm}{0.9}\vspace{0.3cm}

Python, Django \& DRF \hfill\SLIDER{2.5cm}{0.7}\vspace{0.3cm}

PHP \hfill\SLIDER{2.5cm}{0.4}\vspace{0.3cm}

MongoDB \hfill\SLIDER{2.5cm}{0.7}\vspace{0.3cm}

PostgreSQL \hfill\SLIDER{2.5cm}{0.8}\vspace{0.3cm}

Docker \& Kubernetes \hfill\SLIDER{2.5cm}{0.65}\vspace{0.3cm}

.NET \& C\# \hfill\SLIDER{2.5cm}{0.2}\vspace{0.3cm}

Java \& Hibernate \hfill\SLIDER{2.5cm}{0.2}\vspace{0.3cm}

% ===============
% Education
% ===============
\cvsection{Education}


\cvevent{B.Sc. ZFH in Computer Science}{}{Aug. 2011 -- July 2015}{}
Thesis title: Synchronization and Conflict Resolution Strategies in Web Applications
\medskip


\cvevent{Fed. Cert. Information Technology}{}{Sept. 2006 -- July 2010}{}
GBS St.Gallen \& Abacus Research AG



% \cvsection{Languages}
% \cvskill{German}{5}
% \divider

% \cvskill{English}{4}
% \divider

% \cvskill{Japanese}{1}


% ===============
% WB
% ===============
\cvsection{Work before 2016}
\cvevent{SAP consultant / Assistant ICT lead}{Apr. 2011 -- Oct 2015, Loepfe Brothers AG}{}{}
Project stream lead before and during SAP Go-Live and rollout;
supervised and enhanced network security and data protection